Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-26 snapshot_system/fast14_abstract.tex
revisions. moved from inner/cross-VM to local/global dedup

\begin{abstract}
A cloud environment that hosts a large number of virtual machines (VMs) has
a high storage demand for frequent backup of system image snapshots. 
Deduplication of data blocks is necessary to eliminate
redundant blocks and reduce cost. Collocating a cluster-based duplicate service with other cloud services
reduces network traffic;
however, performng global deduplication and letting a data block be shared
by many virtual machines is resource expensive and less fault-resilient. 
This paper proposes a VM-centric collocated backup service that  
localizes deduplication as much as possible within each virtual machine using similarity-guided
search and associates  underlying file blocks with one VM for most cases.
It restricts cross-VM deduplication to popular blocks with extra replication support.
Our analysis shows that  this VM centric scheme 
can  provide  better fault tolerance while using a small amount of computing and storage resources. 
This  paper  describes a comparative evaluation of this scheme in  accomplishing a competitive deduplication 
efficiency while sustaining a good backup throughput. 
\end{abstract}

>>>>

\begin{abstract}
A cloud environment that hosts a large number of virtual machines (VMs) has
a high storage demand for frequent backup of system image snapshots. 
Deduplication of data blocks is necessary to eliminate
redundant blocks and reduce cost. Collocating a cluster-based duplicate service with other cloud services
reduces network traffic;
however, performing global deduplication and letting a data block be shared
by many virtual machines is resource expensive and less fault-resilient. 
This paper proposes a VM-centric collocated backup service that  
localizes deduplication as much as possible within each virtual machine using similarity-guided
search and associates  underlying file blocks with one VM for most cases.
It restricts global deduplication to popular blocks with extra replication support.
Our analysis shows that  this VM centric scheme 
can  provide  better fault tolerance while using a small amount of computing and storage resources. 
This  paper  describes a comparative evaluation of this scheme in  accomplishing competitive deduplication 
efficiency while sustaining a good backup throughput. 
\end{abstract}

### 2013-09-26 snapshot_system/fast14_deduplication.tex

\subsection{Key VC  Strategies}
\label{sect:vc-strategies}
%\begin{itemize}
%\item 
\textbf{VM-specific local duplicate search within similar segments.}
We start with the changed block tracking approach in a coarse grain segment level.
In our implementation with Xen on an Alibaba platform, the segment size is 2MB
and the device driver is extended to support tracking changed segments using a dirty bitmap. 
Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
and cannot afford a small segment size.
It should be noted that dirtybit tracking is supported or can be easily implemented in 
major virtualization solution vendors. For example,
the VMWare hypervisor has an API to let external backup applications know 
the changed areas since last backup. 
The Microsoft SDK provides an API that allows external applications to monitor 
the VM's I/O traffic and implement such changed block tracking feature.

@@

Since the best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{Jin2009},
we conduct additional local similarity guided deduplication on a snapshot by comparing
chunk fingerprints of a dirty segment 
with those in  {\em similar} segments from its parent snapshot. 
We define two segments are similar if their content signature is the same.
This segment content signature value is defined as the minimum value of all its chunk fingerprints 
computed during backup and is recorded in the snapshot metadata (called recipe). Note that this definition of
content similarity is an approximation~\cite{resemblance97}.  When processing a dirty segment,
its  similar segments can be found easily from the
parent snapshot recipe.  Then recipes of the similar segments are loaded to memory,
which contain chunk fingerprints to be compared.
To control the time cost of search, we set a limit on the the number of  similar segments recipes to be fetched. 
% Then,
%given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
%with those in similar segments.  
For a 2MB segment, its segment recipe is roughly 19KB which contains about 500 chunk fingerprints and other chunk metadata,
by limiting at most 10 similar segments to search, the amount of memory for maintaining those similar segment recipes is small.
As part of our local duplicate search we also compare the current segment
against the parent segment at the same offset.

%\item 
\textbf{Global deduplication with popular chunks and replication support.}
This step accomplishes the canonical global fingerprint lookup using a popular fingerprint index.
Our key observation is that the local deduplication has removed most of the duplicates.
There are fewer deduplication opportunities across VMs while the memory and network
consumption for global comparison is more expensive.
Thus our approximation is that the global fingerprint comparison only searches for the top $k$
most popular items. This dataset is called the \textbf{PDS} (popular data set). 
We define chunk popularity as the number of unique copies of the chunk in the data-store,
that is the number of copies of the chunk after local deduplication.
This number can be computed periodically (e.g., on a weekly basis).
Once the popularity of all data chunks is collected, the system only maintains the top $k$
most popular chunk fingerprints (called \textbf{PDS index}) in a distributed shared memory.  
Compared to a preliminary solution which  uses data popularity~\cite{WeiZhangIEEE}, 
this paper provides  a more comprehensive scheme with  improved deduplication efficiency and fault tolerance, and
analytic design guidance.

@@

%\item 
\textbf{VM-centric file system block management.}
When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
accumulate small local chunks. We manage this accumulation process using an log-structured storage scheme built
on a distributed file system discussed in Section~\ref{sect:architecture}.
%Non-PDS chunks from the same VM are stored in one append store. 
Each file system block is either dedicated to non-PDS chunks, or PDS-chunks.
A file system block for non-PDS chunks is associated with one VM and does not contain
any PDS chunks, such that our goal of fault isolation is maintained.
In addition, storing PDS chunks separately allows special replication handling for those popular shared data. 
%%% talk something about snapshot store advantage here? %%%

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|p{1.25cm}|p{5.5cm}|}
\hline
$k$ &  the number of top most popular chunks selected for deduplication\\ 
\hline
$c$ &  the total amount of data chunks in a cluster of VMs\\ 
\hline
$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
\hline
$f_i$ &  the frequency for the $i$th most popular fingerprint\\
\hline
$\delta$ &  the percentage of duplicates detected in local deduplication\\
\hline
$\sigma$ & =$\frac{k}{c_u}$ which is  the percentage of unique data  belonging to  PDS\\
\hline
$p$ & the number of machines in the cluster\\
% \hline
% $V$ & the average number of VMs hosted on each machine\\
\hline
$E_c, E_o$ & deduplication efficiency of VC and VO \\
%\hline
%$D$ & the amount of unique data on each machine\\
%\hline
%$C$ & the average data chunk size. Our setting is  4K.\\
%\hline
%$s$ & the average size of file system blocks in the distributed file system. The default is  64MB.\\
%\hline
%$m$ & memory size on each node used by VC\\ 
%\hline
%$E$ & the size of an popular data index entry\\
\hline
$N_1$ & the average number  of non-PDS file system blocks  in a VM for VC\\
\hline
$N_2$ & the average number  of PDS file system blocks  in a VM for VC\\
\hline
$N_o$ & the average number  of file system blocks  in a VM for VO\\
\hline
A(r) & the availability of a file system block with replication degree $r$\\
\hline
\end{tabular}
\caption{Modeling  parameters}
\label{tab:symbol}
\end{table}

%Table~\ref{tab:symbol} defines paramters $c$, $c_u$, $f_i$, and $\delta$ used below.
%let $c$ be the total number of data chunks. 
%$c_u$ be the total number of fingerprints 
%in the global index after complete deduplication, and
%$f_i$ be the frequency for the $i$th most popular fingerprint. 
By Zipf-like distribution, $f_i = {f_1}/{i^\alpha}.$
The total amount of chunks reside in our backup storage which
has local duplicates excluded is $c (1-\delta)$, this can be represented
as the sum of each unique fingerprint times its frequency:
%Since $ \sum_{i=1}^{c_u}f_i = c (1-\delta)$,
\[
f_1 \sum_{i=1}^{c_u}\frac{1}{i^\alpha} = c (1-\delta).
\]
Given $\alpha <1$, $f_1$ can be approximated with integration:
\begin{equation}
f_1=\frac{c(1-\alpha)(1-\delta)}{c_u^{1-\alpha}}.
\end{equation}

@@

We store the PDS index using a distributed shared memory hashtable such as Memcached
and allocate a fixed percentage of memory space per physical machine for top $k$ popular items.
As the number of physical machines ($p$) increases,
the entire cloud cluster can host more VMs; however,  ratio $\sigma$ which is $k/c_u$ remains
a constant because each physical machine on average still hosts a fixed constant number of 
VMs. Then the overall deduplication efficiency of VC defined in Formula~\ref{eq:dedupeff}
remains constant.
Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.

\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={PDS Coverage},
            width=\linewidth,
            height=0.6\linewidth,
            cycle multi list={
                mline\nextlist
                [3 of]mmark*\nextlist
            },
            %cycle list name=mcolor,
            xlabel={Total num. chunks stored (in billions)},
            ylabel={PDS Coverage (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            %legend pos=outer north east,
            legend columns=2,
            legend style={
                at={(0.5,-0.30)},
            anchor=north},
            ]
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A4] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T4] {figures/cds_coverage.txt};
            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
            \end{axis}
    \end{tikzpicture}
  \caption{Predicted vs. actual PDS coverage as data size increases.}
  \label{fig:cds-coverage}
\end{figure}
Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
chunks detected as duplicates in global deduplication due to PDS.
We call this PDS coverage.
Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
0.65 and measured PDS coverage in our test dataset.
$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for the PDS.
While the predicted value remains flat, PDS  coverage actually increases as more VMs are involved.
increases. This is because actual $\alpha$ value increases with the data size.
%Then  PDS coverage PDS increases as more VMs are involved.

\subsection{ Impact Fault Isolation}

\begin{figure}
    \centering
    \subfigure[Sharing of file blocks under VC]
    {
        \includegraphics[width=3in]{images/share_vc}
        \label{fig:share_vc}
    }
    \\
    \subfigure[Sharing of file blocks under VO]
    {
        \includegraphics[width=3in]{images/share_vo}
        \label{fig:share_vo}
    }
    \caption{Bipartite association of VMs and file blocks under (a) VC and (b) VO. }
    \label{fig:share}
\end{figure}

The replication degree of the backup storage 
is $r$ for regular file blocks and $r=3$ is a typical setting in distributed
file systems~\cite{googlefs03,hdfs10}.
Since $\sigma$ is small (it is 2\% in our experiments),  
the impact of replication on storage increase is very small even 
when we choose a large $r_c/r$ ratio.  For example, $r_c/r=2$ or 3.

@@

Now we  assess  the impact of losing $d$ machines 
to the the VC and VO approaches.  
A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
We use file system blocks rather than a deduplication
data chunk as our unit of failure because the DFS keeps
filesystem blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we derive
the probability of losing a snapshot file block of a VM by
estimating the number of file system blocks per VM in each approach.
As illustrated in Figure~\ref{fig:share},
we build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs in each approach. An association edge is  drawn  from a file block  to a VM 
if this block is used by the VM.

For VC, each VM has an average number of $N_1$ non-PDS file system blocks
and  has  an average of  $N_2$ PDS file system blocks. 
Each non-PDS file system block is associated with one VM
 and  we denote that PDS file system blocks are
shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file block, 
$V$ be the average number of VMs hosted on each machine. Then, 
\[
V *p*N_1 *s  \approx c-E_c(c-c_u) - c_u\sigma\; \mbox{ and } \; 
V *p*N_2 *s  \approx c_u \sigma V_c.
\]

For VO, each VM has an average of $N_o$ file system blocks
and let $V_o$ be the average number of VMs shared by each file system block.
\[
V *p*N_o *s  = (c- E_o(c-c_u) ) V_o.
\]

Since each file block (with default size $64MB$) contains many chunks (on average 4KB),
each file block contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.  Since $c>> c_u$, from the above equations:
\[
\frac{N_1}{N_o} \approx  \frac{1-E_o}{(1-E_c) V_o}.
\] 
When $E_c\approx E_o$ as we demonstrate in Section~\ref{sect:evaldedup}, $N_1$ would be much smaller than $N_o$. 
When there is a failure in file blocks with replication degree $r$
and there is no failure for PDS data with more replicas,   a VM in
the VC approach has a much lower chance to lose a snapshot than VO. 
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
%our test dataset.
%For VC, we only show
%the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
%one VM.
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO. 
From data, we have observed that $N_1$ is much smaller than $N_o$.  
In the evaluation discussed in Section~\ref{ref:evaldedup}, we have considered a worst case scenario that
every PDS file block is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
Even with that, the availability of VC snapshots is much higher than VO and we analyze  this below.
%In fact, $N_1 +N_2 < N_o$. 
%This is likely because the PDS FSBs tightly pack data used by many VMs, 
%which decreases the overall number of FSBs required to backup a VM.
%Note that  if  the backup for multiple VMs were conducted concurrently, there could be many more
%VMs sharing each file block on average in VO.

@@

The full snapshot availability of a VM is estimated as follows with parameters $N_1$ and
 $N_2$ for VC and $N_o$ for VO.
Given normal data replication degree $r$, PDS data replication degree $r_c$, 
the availability of a file system block is the probability that  
all of its replicas do not appear in any group of $d$ failed machines among the total of $p$ machines. 
Namely, we define it as
\[
A(r) = 1-\binom{d}{r}/ \binom{p}{r}. 
\]
Then the availability of one VM's snapshot data under VO approach is the probability that
 all its file system blocks are unaffected during the system failure:
\begin{equation}
\label{eq:VO}
%(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
A(r)^{N_o}. 
\end{equation}

@@

\item
When $r_c \leq d$, both non-PDS and PDS file blocks in VC can have a loss.
The full snapshot availability of  a VM in the VC approach is
\begin{equation}
\label{eq:VC2}
% (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
% *
% (1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
A(r)^{N_1} * A(r_c)^{N_2}
\end{equation}
Table~\ref{tab:fsb-availability} lists the $A(r)$ values with
%that the availability of an individual file system block
with different replication degrees. This demonstrates inequality 
% $1-\frac{ \binom{d}{r}} { \binom{p}{r} } < 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$
$A(r) < A(r_c)$ because of  $r < r_c$.  
Since $N_1$ is much smaller than $N_o$ as discussed previously, 
these two conditions support that VC has a  higher availability. 
%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
\end{itemize}

>>>>

\subsection{Key VC  Strategies}
\label{sect:vc-strategies}
%\begin{itemize}
%\item 
\textbf{VM-specific local duplicate search within similar segments.}
We start with the changed block tracking approach in a coarse grain segment level.
In our implementation with Xen on an Alibaba platform, the segment size is 2MB
and the device driver is extended to support tracking changed segments using a dirty bitmap. 
Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
and cannot afford a small segment size.
It should be noted that dirty bit tracking is supported or can be easily implemented in 
major virtualization solution vendors. For example,
the VMWare hypervisor has an API to let external backup applications know 
the changed areas since last backup. 
The Microsoft SDK provides an API that allows external applications to monitor 
the VM's I/O traffic and implement such changed block tracking feature.

@@

Since the best deduplication uses a non-uniform chunk size 
in the average of 4KB or 8KB~\cite{Jin2009},
we conduct additional local similarity guided deduplication on a snapshot by comparing
chunk fingerprints of a dirty segment 
with those in  {\em similar} segments from its parent snapshot. 
We define two segments are similar if their content signature is the same.
This segment content signature value is defined as the minimum value of all its chunk fingerprints 
computed during backup and is recorded in the snapshot metadata (called recipe). Note that this definition of
content similarity is an approximation~\cite{resemblance97}.  When processing a dirty segment,
its  similar segments can be found easily from the
parent snapshot recipe.  Then recipes of the similar segments are loaded to memory,
which contain chunk fingerprints to be compared.
To control the time cost of search, we set a limit on the number of  similar segments recipes to be fetched. 
% Then,
%given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
%with those in similar segments.  
For a 2MB segment, its segment recipe is roughly 19KB which contains about 500 chunk fingerprints and other chunk metadata,
by limiting at most 10 similar segments to search, the amount of memory for maintaining those similar segment recipes is small.
As part of our local duplicate search we also compare the current segment
against the parent segment at the same offset.

%\item 
\textbf{Global deduplication with popular chunks and replication support.}
This step accomplishes the canonical global fingerprint lookup using a popular fingerprint index.
Our key observation is that the local deduplication has removed most of the duplicates.
There are fewer deduplication opportunities across VMs while the memory and network
consumption for global comparison is more expensive.
Thus our approximation is that the global fingerprint comparison only searches for the top $k$
most popular items. This dataset is called the \textbf{PDS} (popular data set). 
We define chunk popularity as the number of unique copies of the chunk in the data-store,
i.e., the number of copies of the chunk after local deduplication.
This number can be computed periodically, e.g., on a weekly basis.
Once the popularity of all data chunks is collected, the system only maintains the top $k$
most popular chunk fingerprints (called \textbf{PDS index}) in a distributed shared memory.  
Compared to a preliminary solution which  uses data popularity~\cite{WeiZhangIEEE}, 
this paper provides  a more comprehensive scheme with  improved deduplication efficiency and fault tolerance, and
analytic design guidance.

@@

%\item 
\textbf{VM-centric file system block management.}
When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
accumulate small local chunks. We manage this accumulation process using a log-structured storage scheme built
on a distributed file system discussed in Section~\ref{sect:architecture}.
%Non-PDS chunks from the same VM are stored in one append store. 
Each file system block is either dedicated to non-PDS chunks, or PDS-chunks.
A file system block for non-PDS chunks is associated with one VM and does not contain
any PDS chunks, such that our goal of fault isolation is maintained.
In addition, storing PDS chunks separately allows special replication handling for those popular shared data. 
%%% talk something about snapshot store advantage here? %%%

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|p{1.25cm}|p{5.5cm}|}
\hline
$k$ &  the number of top most popular chunks selected for deduplication\\ 
\hline
$c$ &  the total amount of data chunks in a cluster of VMs\\ 
\hline
$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
\hline
$f_i$ &  the frequency for the $i$th most popular fingerprint\\
\hline
$\delta$ &  the percentage of duplicates detected in local deduplication\\
\hline
$\sigma$ & =$\frac{k}{c_u}$ which is  the percentage of unique data  belonging to  PDS\\
\hline
$p$ & the number of machines in the cluster\\
% \hline
% $V$ & the average number of VMs hosted on each machine\\
\hline
$E_c, E_o$ & deduplication efficiency of VC and VO \\
%\hline
%$D$ & the amount of unique data on each machine\\
%\hline
%$C$ & the average data chunk size. Our setting is  4K.\\
%\hline
%$s$ & the average size of file system blocks in the distributed file system. The default is  64MB.\\
%\hline
%$m$ & memory size on each node used by VC\\ 
%\hline
%$E$ & the size of an popular data index entry\\
\hline
$N_1$ & the average number  of non-PDS FSBs in a VM for VC\\
\hline
$N_2$ & the average number  of PDS FSBs in a VM for VC\\
\hline
$N_o$ & the average number  of FSBs  in a VM for VO\\
\hline
A(r) & the availability of an FSB with replication degree $r$\\
\hline
\end{tabular}
\caption{Modeling  parameters}
\label{tab:symbol}
\end{table}

%Table~\ref{tab:symbol} defines paramters $c$, $c_u$, $f_i$, and $\delta$ used below.
%let $c$ be the total number of data chunks. 
%$c_u$ be the total number of fingerprints 
%in the global index after complete deduplication, and
%$f_i$ be the frequency for the $i$th most popular fingerprint. 
By Zipf-like distribution, $f_i = {f_1}/{i^\alpha}.$
The total number of chunks in our backup storage which
has local duplicates excluded is $c (1-\delta)$, this can be represented
as the sum of each unique fingerprint times its frequency:
%Since $ \sum_{i=1}^{c_u}f_i = c (1-\delta)$,
\[
f_1 \sum_{i=1}^{c_u}\frac{1}{i^\alpha} = c (1-\delta).
\]
Given $\alpha <1$, $f_1$ can be approximated with integration:
\begin{equation}
f_1=\frac{c(1-\alpha)(1-\delta)}{c_u^{1-\alpha}}.
\end{equation}

@@

We store the PDS index using a distributed shared memory hash table such as Memcached
and allocate a fixed percentage of memory space per physical machine for top $k$ popular items.
As the number of physical machines ($p$) increases,
the entire cloud cluster can host more VMs; however,  ratio $\sigma$ which is $k/c_u$ remains
a constant because each physical machine on average still hosts a fixed constant number of 
VMs. Then the overall deduplication efficiency of VC defined in Formula~\ref{eq:dedupeff}
remains constant.
Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.

\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={PDS Coverage},
            width=\linewidth,
            height=0.6\linewidth,
            cycle multi list={
                mline\nextlist
                [3 of]mmark*\nextlist
            },
            %cycle list name=mcolor,
            xlabel={Total num. chunks stored (in billions)},
            ylabel={PDS Coverage (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            %legend pos=outer north east,
            legend columns=2,
            legend style={
                at={(0.5,-0.30)},
            anchor=north},
            ]
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A4] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T4] {figures/cds_coverage.txt};
            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
            \end{axis}
    \end{tikzpicture}
  \caption{Predicted vs. actual PDS coverage as data size increases.}
  \label{fig:cds-coverage}
\end{figure}
Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
chunks detected as duplicates in global deduplication due to PDS.
We call this PDS coverage.
Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
0.65 and measured PDS coverage in our test dataset.
$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for the PDS.
While the predicted value remains flat, measured PDS coverage increases as more VMs are involved.
This is because the actual $\alpha$ value increases with the data size.
%Then  PDS coverage PDS increases as more VMs are involved.

\subsection{ Impact on Fault Isolation}

\begin{figure}
    \centering
    \subfigure[Sharing of file system blocks under VC]
    {
        \includegraphics[width=3in]{images/share_vc}
        \label{fig:share_vc}
    }
    \\
    \subfigure[Sharing of file system blocks under VO]
    {
        \includegraphics[width=3in]{images/share_vo}
        \label{fig:share_vo}
    }
    \caption{Bipartite association of VMs and file system blocks under (a) VC and (b) VO. }
    \label{fig:share}
\end{figure}

The replication degree of the backup storage 
is $r$ for regular file system blocks and $r=3$ is a typical setting in distributed
file systems~\cite{googlefs03,hdfs10}.
Since $\sigma$ is small (it is 2\% in our experiments),  
the impact of replication on storage increase is very small even 
when we choose a large $r_c/r$ ratio.  For example, $r_c/r=2$ or 3.

@@

Now we  assess  the impact of losing $d$ machines 
to the VC and VO approaches.  
A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
We use FSBs rather than a deduplication
data chunk as our unit of failure because the DFS keeps
file system blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we derive
the probability of losing a snapshot FSB of a VM by
estimating the number of file system blocks per VM in each approach.
As illustrated in Figure~\ref{fig:share},
we build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs in each approach. An association edge is  drawn  from an FSB to a VM 
if this block is used by the VM.

For VC, each VM has an average number of $N_1$ non-PDS FSBs
and  has  an average of  $N_2$ PDS FSBs. 
Each non-PDS FSB is associated with one VM
 and  we denote that PDS FSBs are
shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file system block, 
$V$ be the average number of VMs hosted on each machine. Then, 
\[
V *p*N_1 *s  \approx c-E_c(c-c_u) - c_u\sigma\; \mbox{ and } \; 
V *p*N_2 *s  \approx c_u \sigma V_c.
\]

For VO, each VM has an average of $N_o$ FSBs
and let $V_o$ be the average number of VMs shared by each FSB.
\[
V *p*N_o *s  = (c- E_o(c-c_u) ) V_o.
\]

Since each FSB (with default size $64MB$) contains many chunks (on average 4KB),
each FSB contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.  Since $c>> c_u$, from the above equations:
\[
\frac{N_1}{N_o} \approx  \frac{1-E_o}{(1-E_c) V_o}.
\] 
When $E_c\approx E_o$ as we demonstrate in Section~\ref{sect:evaldedup}, $N_1$ would be much smaller than $N_o$. 
When there is a failure in FSBs with replication degree $r$
and there is no failure for PDS data with more replicas,   a VM in
the VC approach has a much lower chance to lose a snapshot than VO. 
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
%our test dataset.
%For VC, we only show
%the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
%one VM.
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO. 
From data, we have observed that $N_1$ is much smaller than $N_o$.  
In the evaluation discussed in Section~\ref{ref:evaldedup}, we have considered a worst case scenario that
every PDS FSB is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
Even with that, the availability of VC snapshots is much higher than VO and we analyze  this below.
%In fact, $N_1 +N_2 < N_o$. 
%This is likely because the PDS FSBs tightly pack data used by many VMs, 
%which decreases the overall number of FSBs required to backup a VM.
%Note that  if  the backup for multiple VMs were conducted concurrently, there could be many more
%VMs sharing each file block on average in VO.

@@

The full snapshot availability of a VM is estimated as follows with parameters $N_1$ and
 $N_2$ for VC and $N_o$ for VO.
Given normal data replication degree $r$, PDS data replication degree $r_c$, 
the availability of a file system block is the probability that  
all of its replicas do not appear in any group of $d$ failed machines among the total of $p$ machines. 
Namely, we define it as
\[
A(r) = 1-\binom{d}{r}/ \binom{p}{r}. 
\]
Then the availability of one VM's snapshot data under VO approach is the probability that
 all its FSBs are unaffected during the system failure:
\begin{equation}
\label{eq:VO}
%(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
A(r)^{N_o}. 
\end{equation}

@@

\item
When $r_c \leq d$, both non-PDS and PDS file system blocks in VC can have a loss.
The full snapshot availability of  a VM in the VC approach is
\begin{equation}
\label{eq:VC2}
% (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
% *
% (1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
A(r)^{N_1} * A(r_c)^{N_2}
\end{equation}
Table~\ref{tab:fsb-availability} lists the $A(r)$ values with
%that the availability of an individual file system block
different replication degrees. This demonstrates inequality 
% $1-\frac{ \binom{d}{r}} { \binom{p}{r} } < 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$
$A(r) < A(r_c)$ because of  $r < r_c$.  
Since $N_1$ is much smaller than $N_o$ as discussed previously, 
these two conditions support that VC has a  higher availability. 
%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
\end{itemize}
